Finite Property Convex Elicitation Notes

### 2018-10-01 jessie-writeup/jessie-writeup.tex
Added conjecture about interior and measure

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite.
	Define the property $\Gamma' = \Gamma\cap \R'$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.

@@

	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$
	Since we can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
	\jessie{Need source?}
	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex), contradicts the claim $r_1 \neq r_2$.
	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.

@@

>>>>

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite.
	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \leq \Gamma$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.

@@

	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$
	Since we can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
	\jessie{Need source?}
	As $G$ is concave, it is differentiable almost everywhere, which means that for everywhere but a $\mu$-null set, $|\partial G(p)| = 1$.
	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Conjecture~\ref{conj:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.

@@

\begin{conjecture}\label{conj:pos-measure-iff-nonempty-int}
Let $S$ be a convex set.
$S$ has nonempty interior $\iff S$ has positive Lebesgue measure.
\jessie{I think some details are missing in here, but it gets at the essence.}
\end{conjecture}
\begin{proof}

\begin{enumerate}
\item[$\implies$]
Let $S$ have nonempty interior.
We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
As $0 < \mu(B) \leq \mu(\inter S) = \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.

\item[$\impliedby$]  Follows from the contrapositive and definition of measure.
That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.
If $\mu(\inter{S}) = 0$, then $S$ does not have positive measure.
\end{enumerate}
\end{proof}
